Postural changes mediate children's visual access to social information

### 2018-01-23 writeup-cogsci/cogsci2018_faceOnly.Rmd
plots fixed but still squished

grid.arrange(p1, p1, nrow=2)

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture.""}

>>>>

grid.arrange(p1, p2, nrow=2)

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture."}

### 2018-01-23 writeup-cogsci/cogsci2018_faceOnly.tex
plots fixed but still squished

\caption[Proportion face detections around a naming instance ('Look, a Zem']{Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Each point represents a naming instance for each child in the dataset.}\label{fig:detByNaming}
\end{figure}
\end{CodeChunk}

>>>>

\caption[Proportion face detections around a naming instance ('Look, a Zem']{Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture.}\label{fig:detByNaming}
\end{figure}
\end{CodeChunk}
